Important phase in system development is the successful implementation of the new system
design. Implementation includes all those activities that take place to convert from the old
system to the new system. Project Implementation is a practice of executing or carrying
out a project under a certain plan in order to complete this project and produce desired
results. Such a practice encompasses all processes and activities involved in getting the
project plan fulfilled and accomplishing project goals and objectives. 

Section 5.1 describes
the Algorithm. Software and hardware for development is discussed in detail in Section 5.2.
Section 5.3 describes the various Modules in Project

\section {Algorithm/steps}
Following are the steps that should be carried out for the execution of E-buddy.
\begin{itemize}
\item Start: Display Homepage
\item Complaint Form Registration
\item Registered information to be scrutinised
\item Valid scrutinised information forwarded for verification
\item User Verification done using OTP
\item Scratch cards are availed by users through login
\end{itemize}

\section {Software and Hardware for development in detail}
Following are the hardware and software requirements for E-buddy.
\subsection {Hardware Requirements}
\begin{itemize}
\item \textbf {Dedicated PC/Mobile Phone}: For client side user, it is necessary to connect the
server for reaching the website. To visit the website, user required the dedicated PC,laptop, tablet or Mobile phone. Similarly, this PC also required to developer while
developing the System.
\item \textbf {Internet}: For connecting end user to the developed system, Internet is required. Into
the internet nowadays, the 4G speed Internet is best option for reaching the website
because it generates the interest into the user and view contents of the website in a
efficient manner.
\end {itemize}


\subsection {Software Requirements}
\begin{itemize}
\item \textbf {Browser}: This software does not require a particular Operating System to run but
only a web browser and internet connection because it is a web based application.

\item \textbf {XAMPP}: XAMPP is an easy to install distribution to get in the world of Apache.

\item \textbf {MySQL}: MySQL is a relational database management system based on the Structured Query Language,which is the popular language for accessing and managing the records in the database.
\end{itemize}

\section {Summary}
The above chapter describes the coding and implementation of the project. The next chapter
will discuss the testing methodologies of the project.




